### 2018-05-14 Docs/Thesis/docs/chapter4.tex
*1* ECLIPSE: OXYGEN. *2* MODIFICATION ON THE SIMITAR CODE. NOW RAPIDXML IS LOCATED IN DEPS DIR, AND THE CODE CHANGED A LITTE ON NETWORK TRACE CLASS.

In this chapter, we are going to go into deep details on some implementations and modeling approaches mentioned in the last chapter. In the first section, we are going to discuss our methodology for modeling inter packet-times and validate it as a good choice. The problem we want to address are these:

@@

    \item We have a set of empirical inter-packet times, and some approximate stochastic models that describe it. We want to know what is the best analytically, avoiding human analysis;

    \item We want to know whatever if our modeling approaches are suitable or not to describe inter-packet times.

@@

The gradient descendent consists in minimizing a cost function $J(\theta)$. We explain this procedure in the appendix ~\ref{ap:revision-probability}. In the figure~\ref{fig:linearization} we present as examples, the linearized data for the inter arrivals from the \textit{skype-pcap}, and in the figure ~\ref{fig:linearization-cost} the cost convergence. In the appendix ~\ref{ap:aditional-plots}, a complete set of these figures is presented.

@@

%%%%%%%%%%%%%%%%%%%%%%%
% Logscale Skype
\begin{figure}[ht!]
\centering
\label{fig:aproximation-original-cdf}
\subfloat[Chauchy]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Cauchy_aproximation_vs_Original_set}
}
\subfloat[Exponential(LR)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Exponential_aproximation__linear_regression__vs_Original_set}
}
\hspace{0mm}
\subfloat[Exponential(Me)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Exponential_aproximation__mean__vs_Original_set}
}
\subfloat[Normal]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Normal_aproximation_vs_Original_set}
}
\hspace{0mm}
\subfloat[Pareto(LR)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Pareto_aproximation__linear_regression__vs_Original_set}
}
\subfloat[Pareto(MLH)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Pareto_aproximation__maximum_likehood__vs_Original_set}
}
\hspace{0mm}
\subfloat[Weibull]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Weibull_aproximation_vs_Original_set}
}
\caption{CDF functions for the approximations of \textit{skype-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

@@

Here in this chapter we only discuss the plots achieved obtained by the \textit{pcap} \textit{skype-pcap} for simplicity. The other plots are provided and commented on the appendix ~\ref{ap:aditional-plots}. In the figure ~\ref{fig:aproximation-original-cdf} we present all estimated CDF functions along with the empirical CDF, for the trace \textit{skype-pcap}. They are on log-scale, which provide a better visualization for small time scales. In the case of the normal function, all values smaller than zero were set to zero on the plot. Is possible to see different accuracies and types of fittings on each plot. Visually, the best fit seems to be the Weibull trough linear regression.

@@

All these results are abstracted by the cost function $J$. As we can see, on all pcaps, the best function selected by BIC and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.

@@

@@

@@

We can conclude that using AIC or BIC as criteria for choosing models for inter-packet times is a good choice.

@@

\begin{table}[ht!]
    \centering
    \caption{Application matach table}
    \label{tab:application-protocols}
    \begin{tabular}{lll}
        \hline
        Application Protocol & Transport Protocols & Transport Ports \\ \hline
        HTTPS               & TCP                & 443             \\
        FTP                 & TCP                & 20, 21          \\
        HTTP                & TCP                & 80              \\
        BGP                 & TCP                & 179             \\
        DHCP                & UDP                & 67, 68          \\
        SNMP                & UDP, TCP           & 161             \\
        DNS                 & UDP, TCP           & 53              \\
        SSH                 & UDP, TCP           & 22              \\
        Telnet              & UDP, TCP           & 23              \\
        TACACS              & UDP, TCP           & 49              \\ \hline
    \end{tabular}
\end{table}

>>>>

In this chapter, we are going to go into deep details on some implementations and modeling approaches mentioned in the last chapter. In the first section, we are going to discuss our methodology for modeling inter packet-times, and proof that it is a good choice. But before putting our hands on the problem, we need to precisely define what we want. We abstract our ideas in the bullets below:

@@

    \item Given a set of empiral inter-packet times, we want to parametrize not only one, bua a set of "candidates" stochastic functions to describe it

    \item We want to know, analitically,  which of these candidates is the best, avoiding human analysis;

    \item We need a proof that our choosen analifical analysis is good or not to describe inter-packet times.

@@

The gradient descendent consists in minimizing a cost function $J(\theta)$. We explain this procedure in the appendix ~\ref{ap:revision-probability}. In the figure~\ref{fig:linearization} we present as examples, the linearized data for the inter arrivals from the \textit{skype-pcap}, and in the figure ~\ref{fig:cost} the cost convergence. In the appendix ~\ref{ap:aditional-plots}, a complete set of these figures is presented.

@@

%%%%%%%%%%%%%%%%%%%%%%%
% Logscale Skype
\begin{figure}[ht!]
\centering
\subfloat[Chauchy]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Cauchy_aproximation_vs_Original_set}
}
\subfloat[Exponential(LR)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Exponential_aproximation__linear_regression__vs_Original_set}
}
\hspace{0mm}
\subfloat[Exponential(Me)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Exponential_aproximation__mean__vs_Original_set}
}
\subfloat[Normal]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Normal_aproximation_vs_Original_set}
}
\hspace{0mm}
\subfloat[Pareto(LR)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Pareto_aproximation__linear_regression__vs_Original_set}
}
\subfloat[Pareto(MLH)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Pareto_aproximation__maximum_likehood__vs_Original_set}
}
\hspace{0mm}
\subfloat[Weibull]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Weibull_aproximation_vs_Original_set}
}
\label{fig:aproximation-original-cdf}
\caption{CDF functions for the approximations of \textit{skype-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

@@

Here in this chapter we only discuss the plots achieved obtained by the \textit{pcap} \textit{skype-pcap} for simplicity. The other plots are provided and commented on the appendix ~\ref{ap:aditional-plots}. In the figure~\ref{fig:aproximation-original-cdf} we present all estimated CDF functions along with the empirical CDF, for the trace \textit{skype-pcap}. They are on log-scale, which provide a better visualization for small time scales. In the case of the normal function, all values smaller than zero were set to zero on the plot. Is possible to see different accuracies and types of fittings on each plot. Visually, the best fit seems to be the Weibull trough linear regression.

@@

All these results are abstracted by the cost function $J$. As we can see, on all pcaps, the best function selected by BIC and AIC(table~\ref{tab:prototype-results}) also had the small cost(figure~\ref{fig:cost-function}).

@@

Since there is a lot of information on table~\ref{tab:prototype-results} and on the figure~\ref{fig:cost-function}, we capture just the order of choise form each \textit{pcap} plotted on the figure~\ref{fig:cost-function_vs_aic-bic}. We can see that expecially on the best fittings, the results were closer. Just for the \textit{bigFlows-pcap} the results from the best and second best models were flipped. On all the other cases, the choises were the same. For the worsts models, the results tend to differ more, and loose correlation. It is not a bad thing, since they were not good choices after all.

@@

%validation Cost function
\begin{figure}[t!]
	\centering
	\includegraphics[width=100mm]{figures/ch4/aic-bic_vs_costFunction_order}
	\caption{Comparison of model selection order com cost function and AIC/BIC}
    \label{fig:cost-function_vs_aic-bic}
\end{figure}

@@

We can conclude that using AIC or BIC as criteria for choosing good models for inter-packet times is a good choice.

@@

\begin{table}[ht!]
    \centering
    \caption{Application match table}
    \label{tab:application-protocols}
    \begin{tabular}{lll}
        \hline
        Application Protocol & Transport Protocols & Transport Ports \\ \hline
        HTTPS               & TCP                & 443             \\
        FTP                 & TCP                & 20, 21          \\
        HTTP                & TCP                & 80              \\
        BGP                 & TCP                & 179             \\
        DHCP                & UDP                & 67, 68          \\
        SNMP                & UDP, TCP           & 161             \\
        DNS                 & UDP, TCP           & 53              \\
        SSH                 & UDP, TCP           & 22              \\
        Telnet              & UDP, TCP           & 23              \\
        TACACS              & UDP, TCP           & 49              \\ \hline
    \end{tabular}
\end{table}

### 2018-05-14 Docs/Thesis/docs/chapter5.tex
*1* ECLIPSE: OXYGEN. *2* MODIFICATION ON THE SIMITAR CODE. NOW RAPIDXML IS LOCATED IN DEPS DIR, AND THE CODE CHANGED A LITTE ON NETWORK TRACE CLASS.

The flow's cumulative distribution measures each new flow identified the trace. It is a measure similarity of the traffic at the flow-level.  The wavelet multiresolution analysis is capable of capture traffic scaling characteristics and is a measure of similarity at the packet-level. If the value decreases, a periodicity on that time scale exists. With white-noise features, the traffic will remain constant. If the traffic has self-similar characteristics on a particular time scale, its value will increase linearly.

@@

Libtins enable the creation and emission of arbitrary packets and do not require the establishment of a connection.  Thus SIMITAR does not need to operate in server mode on the destination. The packet customization capability is vast, and enable a full usage of our model parameters. Control inter-packet times stays for future work.

>>>>

The flow's cumulative distribution measures each new flow identified the trace. It is a measure similarity of the traffic at the flow-level.  The wavelet multiresolution analysis is capable of capture traffic scaling characteristics and is a measure of similarity at the packet-level. If the value decreases, a periodicity on that time scale exists. With white-noise features, the traffic will remain constant. If the traffic has self-similar characteristics on a particular time scale, its value will increase linearly. We show a sumary of all performed tests on table~\ref{tab:validation-tests-performed}.

\begin{table}
	\centering
	\label{tab:validation-tests-performed}
	\caption{Performed validations}
		\begin{tabular}{c c}
			\toprule
			\textbf{Metric Type} & \textbf{Validations} \\
			\midrule
			\makecell{Packet Based \\Metrics}                & \makecell{Data bit rate (kbps), Average packet\\
				rate (packets/s), Average packet size\\
				(bytes), Number of packets, Number of\\
				packets, Bandwidth over time}\\

			\makecell{Flow Based \\ Metrics}                & \makecell{Number of flows, Flows per second, \\
				Flows CDF distributions}\\

			\makecell{Fractal and Scaling \\ Characteristics} & \makecell{Hurst Exponent, Wavelet \\
				Multiresolution Analisis}\\
			\bottomrule
		\end{tabular}

@@

Libtins enable the creation and emission of arbitrary packets and do not require the establishment of a connection.  Thus SIMITAR does not need to operate in server mode on the destination. The packet customization capability is vast, and enable a full usage of our model parameters. Control inter-packet times stays for future work~\ref{ch:conclusion}.

### 2018-05-14 Docs/Thesis/docs/chapter6.tex
*1* ECLIPSE: OXYGEN. *2* MODIFICATION ON THE SIMITAR CODE. NOW RAPIDXML IS LOCATED IN DEPS DIR, AND THE CODE CHANGED A LITTE ON NETWORK TRACE CLASS.

\begin{table}[ht!]
    \centering
    \caption{Future Work: task list}
    \label{tab:task-list}
    \begin{tabular}{cccc}
        \hline
        \multicolumn{3}{c}{Future Work}    & Priority \\ \hline
        1   & Optimizing linear regression                       &                                & \textbf{\textit{high}} \\
        2   & Flow-merging option                                &                                & \textit{medium} \\
        3   & Smart flow-scheduler and thread/process management &                                & \textbf{\textit{high}} \\
        4   & \texttt{DataProcessor::minimumAmountOfPackets}     &                                & low \\
        5   & DPDK KNI interfaces                                &                                & \textit{medium} \\
        6   & Multi-thread C++ sniffer                           &                                & \textbf{\textit{high}} \\ 
        7   & Cluster operation (high speed traffic-gen)         & \multirow{-7}{*}{Performance}  & \textbf{\textit{high}} \\ \hline
        8   & Model inter-packet times on \texttt{TinsFlow}      &                                & \textbf{\textit{high}} \\
        9   & D-ITG flow generator (\texttt{DitgFlow})           &                                & low \\
        10  & DPDK flow generator (\texttt{DpdkFlow})            &                                & \textit{medium} \\
        11  & Ostinato flow generator (\texttt{OstinatoFlow})    & \multirow{-4}{*}{Tool support} & low \\ \hline
        12  & \texttt{DataProcessor::min\_time}                  &                                & low \\
        13  & \texttt{DataProcessor::m\_min\_on\_time}           &                                & low \\
        14  & \texttt{DataProcessor::m\_session\_cut\_time}      &                                & low \\
        15  & Minimum number of packets per flow option          & \multirow{-4}{*}{Calibration}  & low \\ \hline
        16  & Python API/Lua for traffic generation              &                                & low \\
        17  & Crafter of  pcap files                             & \multirow{-2}{*}{New features} & low \\

@@

(1) The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor. The performance becomes an issue when processing large \textit{pcap} files with more dozens of thousands of flows. The time expended for processing traces, in this case, is exceeding tens of hours. In the current implementation, the linear regression execution is mono-thread, and the stop criterion is just the number of iterations. Parallel processing, and creating stop criteria based on convergence in addition to the number of iterations will improve the performance, along with some code optimizations.

(2) Crating an option for merging flows is a possibility to improve the performance of traffic with several thousands of flows and Gigabits of bandwidth, such as from WAN captures. A merge criterion, for example, is to consider just network headers on flow's classification.

(3) Currently, all the flow threads are instantiated once the traffic generations start. A smarter traffic generation where SIMITAR instantiates each thread when the traffic, and join when it is inactive should reduce the overhead for traces with a large number of flows. For traffics with a massive amount of streams, a methodology for merging them should reduce computational costs and enable replication of traffic with a much more significant bandwidth. Another improvement in traffic generations is reduced memory consumption per thread and process, and optimize the code.

(4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount. Otherwise, SIMITAR uses the constant model. We decide to do it for two reasons. First, because with a small sample, the modeling accuracy is reduced. Second, we avoid the cost of the parameterization process. Now, its value is set to Its value today is set to 30. Increasing this amount, we may achieve more reasonable performance for individual flows, and reduce the processing time.

(5) One possibility to improve the traffic generation performance issue DPDK Kernel NIC Interface  (KNI interfaces) \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}. DPDK KNI interfaces allow applications from the user's space interact with DPDK ports. In this way, we may achieve a faster packet processing. This can be integrated as an instantiable feature of SIMITAR (figure ~\ref{fig:dpdk-if}).

@@

(6) Another issue is the sniffer component is taking to much time to extract data from large \textit{pcap} files. Implementing a C/C++ multi-thread sniffer, including the packet processing and the SQL queries, will improve its performance.

(7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be split on $m$ separate files, each representing $n/m$ flows, and still portray the same traffic. With $m$ synchronized machines working in parallel, each using one of these $m$ parts of the original \textit{compact trace descriptor}, with use of link-aggregation techinique\footnote{http://www.comutadores.com.br/configurando-link-aggregationetherchannel-entre-cisco-e-hpn/} we can achieve high speeds on bare-metal.

(8) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times. To avoid overheads,  the values of inter-packet times must be calculated before the actual traffic generation. Modeling inter-packet times the scaling characteristics of libtins traffic should improve.

(9-11) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}. D-ITG offers many stochastic functions for customization of inter-packet times, Ostinato provides a rich set of headers and protocols, and DPDK a high performance on packet generation. Each tool can offer a different result on traffic generation, each with benefits and drawbacks, such as computational cost, and development complexity.  Also, DPDK provides the possibility to bypass the Linux network stack, called packet acceleration. So, this implementation can enable for SIMITAR high-bandwidth along with traffic realism.

@@

After this, we search for more solutions and methodologies that could be applied to solve our problems and improve the performance of our prototype. In this procedure, we researched many topics that at the end didn't fit our intentions, such as Machine Learning and Neural Networks. But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed satisfactory. Again, we planned a methodology, procedure, and validate these ideas, as prototypes. Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection. Is it worth?" (in the appendix ~\ref{ap:publications}). Then we research for more related works to gain insights and find platforms and libraries able to fulfill our requirements. In this step, we designed our algorithms presented in chapter ~\ref{ch:modeling-evaluation}, and chose the APIs, packages, and libraries, such as Armadillo\cite{armadillo}, a C++ linear algebra library. Many ideas we used to conceive our ideas were inspired by previous works and solutions, such as D-ITG\cite{ditg-paper}, Harpoon\cite{harpoon-validation}, Swing\cite{swing-paper} sourcesOnoff\cite{sourcesonoff-paper}, and LegoTG\cite{legotg-paper}. This procedure continued with incremental upgrades until we arrived on the version presented on the chapter ~\ref{ch:validation}.

@@

Finally, we created a list of improvements and future works, aiming the development of the software, including, performance better processing time and packet generation, and the realism on the traffic generated. In fact, the higher bottleneck of the project resides on processing performance. The results on realism, even with a lot of room for improvement, already have a good quality. With the proposed future works we believe to be possible overcome the current limitations.

>>>>

\begin{table}[ht!]
    \centering
    \caption{Future Work: task list}
    \label{tab:task-list}
    \begin{tabular}{cccc}
        \hline
        \multicolumn{3}{c}{Future Work}    & Priority \\ \hline
        A1   & Modelling Optimizations                       &                                & \textbf{\textit{high}} \\
        A2   & Flow-merging option                                &                                & \textit{medium} \\
        A3   & Smart flow-scheduler and thread management &                                & \textbf{\textit{high}} \\
        A4   & \texttt{DataProcessor::minimumAmountOfPackets}     &                                & low \\
        A5   & DPDK KNI interfaces                                &                                & \textit{medium} \\
        A6   & Multi-thread C++ sniffer                           &                                & \textbf{\textit{high}} \\ 
        A7   & Cluster operation (high speed traffic-gen)         & \multirow{-7}{*}{Performance}  & \textbf{\textit{high}} \\ \hline
        B1   & Model inter-packet times on \texttt{TinsFlow}      &                                & \textbf{\textit{high}} \\
        B2   & D-ITG flow generator (\texttt{DitgFlow})           &                                & low \\
        B3  & DPDK flow generator (\texttt{DpdkFlow})            &                                & \textit{medium} \\
        B4  & Ostinato flow generator ((\texttt{OstinatoFlow}))            & 						&  \textit{medium}
         \\
        B5  &  Multi-tool flow generator    & \multirow{-5}{*}{Tool support} & low \\ \hline
        C1  & \texttt{DataProcessor::min\_time}                  &                                & low \\
        C2  & \texttt{DataProcessor::m\_min\_on\_time}           &                                & low \\
        C3  & \texttt{DataProcessor::m\_session\_cut\_time}      &                                & low \\
        C4  & Minimum number of packets per flow option          & \multirow{-4}{*}{Calibration}  & low \\ \hline
        D1  & Python and Lua API on the FlowGenerator component             &                                & low \\
        D2  & Crafter of  pcap files                             & \multirow{-2}{*}{New features} & low \\

@@

(A1) The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor. The performance becomes an issue when processing large \textit{pcap} files with more dozens of thousands of flows. The time expended for processing traces, in this case, is exceeding tens of hours. In the current implementation, the linear regression execution is mono-thread, and the stop criterion is just the number of iterations. Parallel processing, and creating stop criteria based on convergence in addition to the number of iterations will improve the performance, along with some code optimizations. Make the XML less verbose should help in this sense as well.

(A2) Crating an option for merging flows is a possibility to improve the performance of traffic with several thousands of flows and Gigabits of bandwidth, such as from WAN captures. A merge criterion, for example, is to consider just network headers on flow's classification.

(A3) Currently, all the flow threads are instantiated once the traffic generations start. A smarter traffic generation where SIMITAR instantiates each thread when the traffic, and join when it is inactive should reduce the overhead for traces with a large number of flows. For traffics with a massive amount of streams, a methodology for merging them should reduce computational costs and enable replication of traffic with a much more significant bandwidth. Another improvement in traffic generations is reduced memory consumption per thread and process, and optimize the code.

(A4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount. Otherwise, SIMITAR uses the constant model. We decide to do it for two reasons. First, because with a small sample, the modeling accuracy is reduced. Second, we avoid the cost of the parameterization process. Now, its value is set to Its value today is set to 30. Increasing this amount, we may achieve more reasonable performance for individual flows, and reduce the processing time.

(A5) One possibility to improve the traffic generation performance issue DPDK Kernel NIC Interface  (KNI interfaces) \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}. DPDK KNI interfaces allow applications from the user's space interact with DPDK ports. In this way, we may achieve a faster packet processing. This can be integrated as an instantiable feature of SIMITAR (figure ~\ref{fig:dpdk-if}).

@@

(A6) Another issue is the sniffer component is taking to much time to extract data from large \textit{pcap} files. Implementing a C/C++ multi-thread sniffer, including the packet processing and the SQL queries, will improve its performance.

(A7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be split on $m$ separate files, each representing $n/m$ flows, and still portray the same traffic. With $m$ synchronized machines working in parallel, each using one of these $m$ parts of the original \textit{compact trace descriptor}, with use of link-aggregation techinique\footnote{http://www.comutadores.com.br/configurando-link-aggregationetherchannel-entre-cisco-e-hpn/} we can achieve high speeds on bare-metal.

(B1) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times. To avoid overheads,  the values of inter-packet times must be calculated before the actual traffic generation. Modeling inter-packet times the scaling characteristics of libtins traffic should improve.

(B2-B5) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}. D-ITG offers many stochastic functions for customization of inter-packet times, Ostinato provides a rich set of headers and protocols, and DPDK a high performance on packet generation. Each tool can offer a different result on traffic generation, each with benefits and drawbacks, such as computational cost, and development complexity.  Also, DPDK provides the possibility to bypass the Linux network stack, called packet acceleration. So, this implementation can enable for SIMITAR high-bandwidth along with traffic realism. Finally, a multi-tool FlowGenerator is possible as well, using different sorts of lybraries and tools for producing certains types of flows. For example, using SURGE\cite{surge-paper} to create HTTP flows, and Libtins to produce UDP flows.

@@

After this, we search for more solutions and methodologies that could be applied to solve our problems and improve the performance of our prototype. In this procedure, we researched many topics that at the end didn't fit our intentions, such as Machine Learning and Neural Networks. But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed satisfactory. Again, we planned a methodology, procedure, and validate these ideas, as prototypes. Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection. Is it worth?" (in the appendix ~\ref{ap:publications}). Then we research for more related works to gain insights and find platforms and libraries able to fulfill our requirements. In this step, we designed our algorithms presented in chapter ~\ref{ch:modeling-evaluation}, and chose the APIs, packages, and libraries, such as Armadillo\cite{armadillo}, a C++ linear algebra library. Many ideas we used to conceive our problems were inspired by previous works and solutions, such as D-ITG\cite{ditg-paper}, Harpoon\cite{harpoon-validation}, Swing\cite{swing-paper} sourcesOnoff\cite{sourcesonoff-paper}, and LegoTG\cite{legotg-paper}. This procedure continued with incremental upgrades until we arrived on the version presented on the chapter ~\ref{ch:validation}.

@@

Finally, we created a list of improvements and future works, aiming the development of the software, including, performance better processing time and packet generation, and the realism on the traffic generated. In fact, the higher bottleneck of the project resides on processing performance. For processing huges \textit{pcap} files, it still takes a prohibitive amount of time. The results on realism, even with a lot of room for improvement, already have a good quality. With the proposed future works we believe to be possible overcome the current limitations.
